---
title: "Dataset_description"
output: html_document
date: "2023-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Description

The dataset *mbs_circular.RData* is located in the *objects* folder. It contains information about various attributes of a study involving participants, their responses, and video stimuli.

#### Loading the Dataset

To load the dataset *mbs_circular.RData* into R, you can use the following code:

```{r , echo=TRUE, eval = FALSE}
# Load the dataset
load("moebius_circular.RData")
```

After executing the code, 4 the datasets will be loaded into your R environment and will be accessible for further analysis and exploration.

1. `coords`: Genova Emotion Wheel references.

2. `dataset_full`: Contains all information about various attributes of a study involving participants, their responses, and video stimuli. The dataset consists of 4,388 rows and 25 columns.

3. `dataset_gw1`: Fltered version of `dataset_full` restricted to GW1 task's trials without neutral videos. The dataset consists of 1824 rows and 25 columns.

4. `dataset_neutral`: Filtered version of `dataset_full` restricted to GW1 task's trials only with neutral videos.


### Experiment Columns

1. `Exp.trial`: 
   - Variable: Exp.trial
   - Description: The trial number of the experiment (numeric). This column represents the specific trial number within the experiment.
   - Type: Numeric

2. `Exp.notes`: 
   - Variable: Exp.notes
   - Description: Additional notes or information related to the experiment.
   - Type: Character

3. `Exp.date`: 
   - Variable: Exp.date
   - Description: The date of the experiment (Date format: YYYY-MM-DD). This column provides information about when the experiment took place.
   - Type: Date


#### Participant Columns

1. `Pt.study`: 
   - Variable: Pt.study
   - Description: The number of years the participant has studied (numeric). This column represents the duration of education for each participant, starting from their school years to university or higher education.
   - Type: Factor

2. `Pt.id`: 
   - Variable: Pt.id
   - Description: The ID of the participant (factor with 19 levels). This column contains the unique IDs assigned to each participant.
   - Type: Factor

3. `Pt.group`: 
   - Variable: Pt.group
   - Description: The group to which the participant belongs (factor with 2 levels: "control" and "moebius"). This column categorizes the participants into control or Moebius groups.
   - Type: Factor

4. `Pt.gender`: 
   - Variable: Pt.gender
   - Description: The gender of the participant (factor with 2 levels: "female" and "male"). This column indicates the gender of each participant.
   - Type: Factor

5. `Pt.code`: 
   - Variable: Pt.code
   - Description: The participant code, representing different categories (factor with 19 levels). This column contains codes assigned to different participants, indicating their specific category.
   - Type: Factor

6. `Pt.age`: 
   - Variable: Pt.age
   - Description: The age of the participant (numeric). This column provides the age of each participant.
   - Type: Numeric

#### Response Columns

1. `Resp.level`: 
   - Variable: Resp.level
   - Description: The intensity level of the response (character). This column represents the level of the response (based on GEW dots).
   - Type: Factor

2. `Resp.intensity`: 
   - Variable: Resp.intensity
   - Description: The intensity of the response (numeric). This column represents the intensity of the response in px.
   - Type: numeric

3. `Resp.diff`: 
   - Variable: Resp.diff
   - Description: The angle difference (numeric). This column represents the angle difference between the Resp.angle and Wheel.angle.
   - Type: numeric

4. `Resp.correct`: 
   - Variable: Resp.correct
   - Description: Indicator if the response was correct (1 = correct, 0 = incorrect). not applicable to GW2.
   - Type: Logical

5. `Resp.category`: 
   - Variable: Resp.category
   - Description: The emotion category of the response (Factor). This column represents the category of the response.
   - Type: Factor

6. `Resp.angle`: 
   - Variable: Resp.angle
   - Description: The response angle (numeric). This column represents the angle of the response on the GEW.
   - Type: Numeric
   
7. `Resp.rt`: 
   - Variable: Wheel.rt
   - Description: The response time of the wheel (numeric). This column records the response time in milliseconds for each wheel response.
   - Type: Numeric

#### Video Stimuli Columns

1. `Video.set`:
   - Variable: Video.set
   - Description: The set of the video stimulus (factor with 2 levels: "ADFES" and "JeFEE"). This column categorizes the video stimuli into different sets.

#### Genova Emotional Wheel Columns
   - Type: Factor

2. `Video.name`: 
   - Variable: Video.name
   - Description: The name of the video stimulus (factor with 62 levels). This column contains the names of different video stimuli used in the experiment.
   - Type: Factor

3. `Video.id`: 
   - Variable: Video.id
   - Description: The ID of the video stimulus (factor with 9 levels). This column contains the unique IDs assigned to each video stimulus.
   - Type: Factor

4. `Video.gender`: 
   - Variable: Video.gender
   - Description: The gender associated with the video stimulus (factor with 2 levels: "female" and "male"). This column indicates the gender associated with the each video actor.
   - Type: Factor

5. `Video.emotion`: 
   - Variable: Video.emotion
   - Description: The emotion associated with the video stimulus (factor with 16 levels). This column represents the emotion category associated with each video stimulus (satisfaction, happiness, elation, pride, anger, contempt, disgust, envy, guilt, shame, fear, sadness, surprise, interest, hope, relief).
   - Type: Factor

#### Genova Emotional Wheel Columns

1. `Wheel.x`, `Wheel.y`: 
   - Variable: Wheel.x
   - Description: The mouse x or y postions (numeric). 
   - Type: Numeric

2. `Wheel.task`: 
   - Variable: Wheel.task
   - Description: The task performed on the wheel (factor with 2 levels: "practice" and "task").
   - Type: Factor

3.  `Wheel.name`: 
   - Variable: Wheel.name
   - Description: The name of the wheel (factor with 2 levels: "GW1" and "GW2"). This column contains the names of Genova emotional wheels used in the experiment. GW1 is used to indicates the principal emotion seen in the video, GW2 is used to indicate a secondary emotion.
   - Type: Factor

4. `Wheel.angle`: 
   - Variable: Wheel.angle
   - Description: The angle of the Genova emotional wheel (numeric). This column represents the angle reference of the Genova emotional wheel.
   - Type: Numeric

#### Treatment Columns

1. `Trt.physio`: 
   - Variable: Trt.physio
   - Description: Physiological Treatment of palsy.
   - Type: Factor

2. `Trt.botulino`: 
   - Variable: Trt.botulino
   - Description: Botulism treatment.
   - Type: Factor

#### Smile surgery Columns

1. `Surg.type`: 
   - Variable: Surg.type
   - Description: Type of surgery.
   - Type: character

2. `Surg.smile`: 
   - Variable: Surg.smile
   - Description: Indicator if a smile surgery was performed.
   - Type: Logical

3. `Surg.inter`: 
   - Variable: Surg.inter
   - Description: Locus of the surgery.
   - Type: character

4. `Surg.date`:
   - Variable: Surg.date
   - Description: Date of surgery.
   - Type: int
   
#### Palsy Columns

1. `Plsy.locus.note`: 
   - Variable: Plsy.locus.note
   - Description: Notes related to the Plsy.locus column.
   - Type: Character

2. `Plsy.locus`: 
   - Variable: Plsy.locus
   - Description: Palsy locus.
   - Type: Character

3. `Plsy.act.sup3`: 
   - Variable: Plsy.act.sup3
   - Description: Palsy activity superior to 3.
   - Type: Character

4. `Plsy.act.inf2`: 
   - Variable: Plsy.act.inf2
   - Description: Palsy activity inferior to 2.
   - Type: Character
   
#### Assesment's Columns

1. `Asmt.tas.20`:
   - Variable: Asmt.tas.20
   - Description: TAS-20 total.
   - Type: Numeric

2. `Asmt.sunnybrook.note`: 
   - Variable: Asmt.sunnybrook.note
   - Description: Notes related to the Sunnybrook assessment.
   - Type: Numeric

3. `Asmt.sunnybrook`: 
   - Variable: Asmt.sunnybrook
   - Description: The Sunnybrook test score for each participant (numeric). This column contains a numeric value representing the score achieved by each participant on the Sunnybrook test.
   - Type: Numeric

4. `Asmt.omft`:
   - Variable: Asmt.omft
   - Description: Total score of the OFMT assessment.
   - Type: Numeric

5. `Asmt.lpost.tot`: 
   - Variable: Asmt.lpost.tot
   - Description: Total score of the l-post assessment.
   - Type: Numeric

6. `Asmt.lpost.01` to `Asmt.lpost.15`: 
   - Variables: Asmt.lpost.01, Asmt.lpost.02, ..., Asmt.lpost.14, Asmt.lpost.15
   - Description: Individual scores of the lpost assessment.
   1. Fine shape discrimination
   2. Dot lattices
   3. RFP contour integration
   4. Shape ratio discrimination (Efron)
   5. Figure ground segmentation
   6. Kinetic object segmentation
   7. RFP texture surfaces
   8. RFP Fragmented outline
   9. Biological motion
   10. Recognition of missing parts
   11. Global motion detection
   12. Dot counting
   13. Recognition of objects in isolation
   14. Embedded figure detection
   15. Recognition of objects in scene
   - Type: Numeric

7. `Asmt.fdi.sociale`: 
   - Variable: Asmt.fdi.sociale
   - Description: FDI sociale assessment.
   - Type: Numeric

8. `Asmt.fdi.fisica`: 
   - Variable: Asmt.fdi.fisica
   - Description: FDI physical assessment.
   - Type: Numeric

9. `Asmt.aq`: 
   - Variable: Asmt.aq
   - Description: AQ assessment.
   - Type: Numeric
 
 
