---
title: "**CARIPARO MBS vs control**"
subtitle: "Accuracy AUs"
author: 
  - "Thomas Quettier"
# output: html_document
output: bookdown::html_document2
header-includes:
- \usepackage{floatrow}
- \usepackage{subfig}

date: "2023-05-16"
---
<style type="text/css">
   .main-container {max-width: 100%;}
   .row {display: flex;}
   .column {flex: 50%;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, cache=FALSE,include=FALSE}
devtools::load_all()
```

```{r data, include=FALSE}

load("../objects/mbs_circular.RData")
# Calculate mean intensity
correct_data <-  dataset_gw1 %>%
  dplyr::select(Pt.code, Pt.match, Video.set, Video.emotion, Pt.group, Resp.correct) %>%
  'colnames<-'(c("subject" ,"match","video_set", "emotion", "group", "correct"))

accuracy<-correct_data%>%
  group_by(subject,match,group, emotion, video_set) %>%
  summarise(correct = sum(correct),
            acc = correct/8) # 8 = 4 video id * 2 blocks

au_deficit <- c("happiness","surprise","sadness","fear","disgust","anger")


```

## Accuracy

For the accuracy responses, we fit generalized linear models (glmer),  using lme4 R package (v.1.1-33; Douglas & al. (2023)).We regressed participants’ correct responses (1 = success, 0 = error ) on these sets of regressors [correct ∼ emotion * group * video_set +  (1 |ID)] 

<!-- and computed significance levels for the fixed and random effects using the “Anova” function using car R package (v.3.1-2; Fox & al. (2023)), which returns p-values via the likelihood ratio tests. -->


## Satistics
\n
### Correct ~ group + (1|subject)

## anger

```{r anger, include=FALSE}

deficit <- au_deficit[6] # anger
selection <- au_compromition(deficit)
  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitAF)
  pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  
  x<-x%>% 
    filter(subject != "5_moebius", subject != "7_moebius",subject != "8_moebius", subject != "10_moebius")

  fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitA)
  pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitAF),main = "anger ADFES all subjects",
     sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJF),main = "anger JeFEE all subjects",
     sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "anger ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "anger JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

## disgust

```{r disgust, include=FALSE}

deficit <- au_deficit[5] # disgust
selection <- au_compromition(deficit)

  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitAF)
  pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  
  x<-x%>% filter(subject != "5_moebius",subject != "7_moebius",subject != "8_moebius")

  fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitA)
  pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitAF),main = "disgust ADFES all subjects",
     sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJF),main = "disgust JeFEE all subjects",
     sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "disgust ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "disgust JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

## fear

```{r fear, include=FALSE}

deficit <- au_deficit[4] # fear
selection <- au_compromition(deficit)

  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitAF)
  pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  
  x<-x%>% 
    filter(subject != "3_moebius",subject != "4_moebius",subject != "6_moebius",subject != "7_moebius",subject != "8_moebius",subject != "10_moebius")

  fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitA)
  pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitAF),main = "fear ADFES all subjects",
     sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJF),main = "fear JeFEE all subjects",
     sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "fear ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "fear JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

## sadness

```{r sadness, include=FALSE}

deficit <- au_deficit[3] # sadness
selection <- au_compromition(deficit)

  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitAF)
  pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  
  x<-x%>% filter(subject != "5_moebius", subject != "7_moebius", subject != "8_moebius", subject != "10_moebius")

  fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitA)
  pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitAF),main = "sadness ADFES all subjects",
     sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJF),main = "sadness JeFEE all subjects",
     sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "sadness ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "sadness JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

## Happiness

```{r Happiness, include=FALSE}

deficit <- au_deficit[1] # happiness
selection <- au_compromition(deficit)

  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitAF)
  pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  
  x<-x%>% filter(subject != "1_moebius", subject != "3_moebius", subject != "4_moebius",subject != "6_moebius",subject != "7_moebius",subject != "8_moebius",subject != "9_moebius",subject != "10_moebius")

  fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  p<-summary(fitA)
  pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitAF),main = "Happiness ADFES all subjects",
     sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJF),main = "Happiness JeFEE all subjects",
     sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "Happiness ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "Happiness JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

## surprise

```{r surprise, include=FALSE}

deficit <- au_deficit[2] # surprise
selection <- au_compromition(deficit)

  # Adatta il modello di regressione logistica
  x<-correct_data%>%
    mutate(correct = as.factor(correct),
           video_set = as.factor(video_set))%>%
    na.omit()%>% filter(emotion == deficit)

  #fitAF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  fitJF <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  # p<-summary(fitAF)
  # pvalAF<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJF)
  pvalJF<- round(p$coefficients[2,4],3)
  


  # fitA <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "ADFES"), family = binomial)
  
  fitJ <- glmer(correct ~ group  + (1|subject) , data = x%>%filter(video_set == "JeFEE"), family = binomial)
  
  
  # p<-summary(fitA)
  # pvalA<- round(p$coefficients[2,4],3)
 
  p<-summary(fitJ)
  pvalJ<- round(p$coefficients[2,4],3)

```
included: MBS `r na.omit(selection)`

\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

# plot(allEffects(fitAF),main = "surprise ADFES all subjects",
#      sub=paste0("p.value = ",pvalAF))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
# plot(allEffects(fitJF),main = "surprise JeFEE all subjects",
#      sub=paste0("p.value = ",pvalJF))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4,  echo = F,  warning=FALSE,message=FALSE}

plot(allEffects(fitA),main = "surprise ADFES selected",
     sub=paste0("p.value = ",pvalA))
```
  </div>
  <div class = "column">
```{r,fig.width=3,fig.height=4, echo = F,  warning=FALSE,message=FALSE}
plot(allEffects(fitJ),main = "surprise JeFEE selected",
     sub=paste0("p.value = ",pvalJ))
```
  </div>
  <div class="col-lg-2">
  </div>
</div>
