---
title: "**CARIPARO online student**"
subtitle: "Accuracy"
author: 
  - "Thomas Quettier"
# output: html_document
output: bookdown::html_document2
header-includes:
- \usepackage{floatrow}
- \usepackage{subfig}

date: "2023-07-11"
---
<style type="text/css">
   .main-container {max-width: 100%;}
   .row {display: flex;}
   .column {flex: 50%;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, cache=FALSE,include=FALSE}
devtools::load_all()
```

```{r data, include=FALSE}

load("../objects/online_circular.RData")
load("../models/accuracy.RData")
load("../objects/online_info.RData")
```

## Accuracy

For the accuracy responses, we fit generalized linear models (glmer),  using lme4 R package (v.1.1-33; Douglas & al. (2023)).We regressed participants’ correct responses (1 = success, 0 = error ) on these sets of regressors [correct ∼ emotion * group * video_set +  (1 |ID)] and computed significance levels for the fixed and random effects using the “Mixed” function using afex R package (v.1.3-0; Singmann & al. (2016)), which returns p-values via the likelihood ratio tests.

<br/>
```{r, pttab, echo = F, out.width="100%",  warning=FALSE,message=FALSE}
demogaphic_tbl_summary
```
Table 2.1 represents participants' GW1 accuracy responses. 

<br/>
```{r, acctab, echo = F, out.width="100%",  warning=FALSE,message=FALSE}
table_accuracy
```
Table 2.1 represents participants' GW1 accuracy responses. 
<br/>

```{r, accfig1, fig.width=10,fig.height=7,echo = F, fig.cap = "Represents participants' GW1 responses mean frequencies. x = GEW labels, y = video emotion seen", warning=FALSE,message=FALSE, fig.align='center'}
plot_freq_gw1
```
<br/>

```{r, accfig2,fig.width=10,fig.height=7, echo = F, fig.cap = "Represents participants' GW2  responses frequencies. x = GEW labels, y = video emotion seen", warning=FALSE,message=FALSE, fig.align='center'}
plot_freq_gw2
```
<br/>

```{r, Wheelresp,fig.width=10,fig.height=7, echo = F, fig.cap = "Represents participants' GEW 1 responses ", warning=FALSE,message=FALSE, fig.align='center'}
plot_gew_emotions_gw1
```
<br/>

```{r, matrix,fig.width=10,fig.height=7, echo = F, fig.cap = "Represents participants' GW1  % responses distributution. x = GEW labels, y = video emotion seen", warning=FALSE,message=FALSE, fig.align='center'}
matrix_confusion
```
<br/>

<!-- ## Satistics -->
<!-- \n -->
<!-- ### Correct ~ emotion * video_set * group + (1|subject) -->
<!-- \n -->
<!-- <br/> -->
<!-- <div class = "row"> -->
<!--   <div class = "col col-lg-2"> -->
<!--   \n -->
<!--   </div> -->
<!--   <div class = "column"> -->
<!-- ```{r,  echo = F,  warning=FALSE,message=FALSE} -->

<!-- LRT_table -->
<!-- contrast -->
<!-- ``` -->
<!--   </div> -->
<!--   <div class = "column"> -->
<!-- ```{r,fig.width=6,fig.height=12, echo = F,  warning=FALSE,message=FALSE} -->
<!-- ploteffect -->
<!-- ``` -->
<!--   </div> -->
<!--   <div class="col-lg-2"> -->
<!--   </div> -->
<!-- </div> -->


<!-- ```{r,fig.height=15, echo = F,  warning=FALSE,message=FALSE, fig.align='center'} -->
<!-- plot_gew_emotions_gw1 -->
<!-- ``` -->

<!-- ```{r,fig.width=6,fig.height=6, echo = F,  warning=FALSE,message=FALSE, fig.align='center'} -->
<!-- gew_legend -->
<!-- ``` -->
<!-- <br/> -->