---
title: "**CARIPARO Palsy vs control**"
subtitle: "Percived Intensity"
author: 
  - "Thomas Quettier"
# output: html_document
output: bookdown::html_document2
header-includes:
- \usepackage{floatrow}
- \usepackage{subfig}

date: "2023-05-16"
---
<style type="text/css">
   .main-container {max-width: 100%;}
   .row {display: flex;}
   .column {flex: 50%;}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, cache=FALSE,include=FALSE}
devtools::load_all()
```

```{r data, include=FALSE}

load("../objects/palsy_circular.RData")
load("../models/perceived_intensity.RData")
```

## Perceived Intensity

For the intensity responses, we Fit a linear mixed-effects model (LMM) to data, via maximum likelihood. We used lme4 R package [v1.1-33; @lme4].We regressed participants’ intensity for correct responses on these sets of regressors [intensity ∼ emotion * group * video_set +  (1 |ID)] and computed significance levels for the fixed and random effects using the “anova” function, which returns a Type III ANOVA table with significance levels. We used Phia R package [v0.2-1; Rosario-Martinez (2015)].

<br/>

```{r, acctab, echo = F, out.width="100%",  warning=FALSE,message=FALSE}
table_intensity
```
Table 2.1 represents participants' GW1 percieived intensity responses. 
<br/>

```{r, accfig1, fig.width=10,fig.height=7,echo = F, fig.cap = "Represents participants' GW1 responses mean perceived intensity", warning=FALSE,message=FALSE, fig.align='center'}
plot_emotion
```
<br/>


## Satistics
\n
### intensity ~ emotion * video_set * group + (1|subject)
\n
<br/>
<div class = "row">
  <div class = "col col-lg-2">
  \n
  </div>
  <div class = "column">
```{r,  echo = F,  warning=FALSE,message=FALSE}

chi_table

contrast
```
  </div>
  <div class = "column">
```{r,fig.width=6,fig.height=12, echo = F,  warning=FALSE,message=FALSE}
ploteffect
```
  </div>
  <div class="col-lg-2">
  </div>
</div>

<br/>